% file:     main.tex
% created:  2018-12-26 10:45
% author:   Bryant Finney <bryant.finney@uah.edu>
\documentclass[10pt,a4paper]{article}

% Comment the following line to deny the usage of umlauts and other non-ASCII characters
\usepackage[latin1]{inputenc}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}

\newcommand{\csection}[1]{\Large\textbf{#1}}
\newcommand{\csubsection}[1]{\large\textbf{#1}}

\geometry{
  a4paper,          % redundant (already in \documentclass)
  left=0.5in,
  right=0.5in,
  top=0.5in,
  bottom=0.90in,
  heightrounded,    % better use it
}

\usepackage{standalone}
\usepackage{import}

\begin{document}
\begin{table}
  \noindent\begin{tabularx}{\textwidth}{Xr|l}
    \toprule
    \multirow{2}{*}{\Huge Bryant Finney} & 1306 Randolph Ave SE, APT 2A & \href{mailto:finneybp@gmail.com}{finney.bp@gmail.com} \\
                                         & Huntsville, Al 35801         & \href{tel:1-256-714-1289}{256-714-1289}               \\
    \bottomrule
  \end{tabularx}
\end{table}

A jack-of-all-trades with a wide experience base, I have a driven passion for crossing
the hardware/software boundaries and developing full-stack software and sensor solutions.

\bigskip

\noindent\begin{tabularx}{\textwidth}{Xr}
  \csection{Employment History} & \\
\end{tabularx}
\smallskip

\noindent\begin{tabularx}{\textwidth}{Xr}
  \toprule
  \csubsection{OutdoorLink, Inc.} & 2019 February - Present                                   \\
  \textit{Lead Software Engineer} & \href{http://smartlinkcontrol.com/}{smartlinkcontrol.com} \\
\end{tabularx}
\smallskip

\import{odl/}{intro.tex}

\bigskip

\import{odl/devops/}{devops.tex}
\import{odl/fullstack/}{fullstack.tex}

\bigskip

\noindent\begin{tabularx}{\textwidth}{Xr}
  \toprule
  \csubsection{IERUS Technologies, Inc.} & 2016 October - 2019 February                     \\
  \textit{Engineer}                      & \href{https://www.ierustech.com/}{ierustech.com} \\
\end{tabularx}
\smallskip

I performed software development and engineering analysis on more than ten defense
contracts. Software development was done both independently and as part of an agile
scrum team.

\bigskip

\import{ierus/tpt/}{tpt.tex}
\import{ierus/dash/}{dash.tex}
\import{ierus/ccp/}{ccp.tex}
\import{ierus/maatc/}{maatc.tex}

\noindent\begin{tabularx}{\textwidth}{Xr}
  \toprule
  \csubsection{RMCI, Inc.}           & 2012 August - 2016 October                     \\
  \textit{Embedded Systems Engineer} & \href{https://www.rmci-inc.com/}{rmci-inc.com} \\
\end{tabularx}
\smallskip

I started as an intern during my last year of undergrad, and I was hired as a full-time
engineer upon graduation. Initially focused on mechanical and aerospace product
development, I transitioned to embedded system development as the opportunity arose; this
included software, firmware, and hardware design, implementation, and testing.

\bigskip

\import{rmci/}{rmci.tex}

\noindent\begin{tabularx}{\textwidth}{Xr}
  \toprule
  \csubsection{University of Alabama in Huntsville} & 2012 February - 2012 December                     \\
  \textit{Research Assistant}                       & \href{https://www.uah.edu/smap}{www.uah.edu/smap} \\
\end{tabularx}

\import{uah/}{ra.tex}

\noindent\begin{tabularx}{\textwidth}{Xr}
  \toprule
  \csubsection{University of Alabama in Huntsville}            & 2010 August - 2012 December                               \\
  \textit{Peer-Assisted Study Session (PASS) Leader and Tutor} & \href{https://www.uah.edu/ssc/pass}{www.uah.edu/ssc/pass} \\
\end{tabularx}

\import{uah/}{pass.tex}

\noindent\begin{tabularx}{\textwidth}{Xr}
  \csection{Education} & \\
  \bottomrule
\end{tabularx}
\smallskip

\noindent\begin{tabularx}{\textwidth}{cccXr}
  \multicolumn{3}{l}{The University of Alabama in Huntsville} &                       & 2009 - 2013                        \\
  \multicolumn{5}{l}{\hspace{.125in} Bachelor's of Science in Mechanical Engineering}                                      \\
  \hspace{.125in} \textit{suma cum laude}                     & \textit{pi tau sigma} & \textit{tau beta pi} &  & GPA: 4.0 \\
\end{tabularx}
\bigskip

\end{document}
